### 2012-03-01 docs/SDC/sdc.tex
new notation

{\bf Step 1B:} ({\it Compute advective fluxes}) Use $\uadvsdcpred$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf,{\rm pred}}$, with time-lagged reactions, explicit diffusion, and time-centered thermodynamic pressure as source terms.\\

{\bf Step 1C:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}}X_{k,{\rm AD}}^{n+1,{\rm pred}} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + I_{\rho X_k}^{\rm lagged}.\label{eq:sdc species 2}
\end{equation}
Then, solve a Crank-Nicolson-type diffusion equation for $h^{n+1,{\rm pred}}_{\rm AD}$, using transport coefficients evaluated at $t^n$ everywhere,
\begin{eqnarray}
\frac{\rho^{n+1,{\rm pred}}h^{n+1,{\rm pred}}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + \uadvsdcpred\cdot\nabla p_0 + I_{\rho h}^{\rm lagged}\nonumber\\
&& + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n + \nabla\cdot\frac{\kth^n}{c_p^n}\nabla h_{\rm AD}^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_{k,{\rm AD}}^{n+1,{\rm pred}}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0\right).\label{eq:sdc enthalpy 2}
\end{eqnarray}

{\bf Step 1D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}^{\rm pred}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{\rho X_k}^{\rm lagged}$ term, and define $Q_{\rho h}^{\rm pred}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{\rho h}^{\rm lagged}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,{\rm pred}}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{\rm pred} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{\rm pred} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{\rm pred}$ and $I_{\rho h}^{\rm pred}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the corrector step.\\

{\bf Step 2:} ({\it Corrector}) In the corrector, we use the time-advanced state from the predictor to perform a more accurate integration of the thermodynamic variables.  The quantities $(S, \beta_0, k_{\rm th}, c_p, \xi_k, h_p)^{n+1,{\rm pred}}$ are computed from $(\rho,\rho X_k,\rho h)^{n+1,{\rm pred}}$.  This step is divided into several sub-steps:\\\\

{\bf Step 2A:} ({\it Compute advection velocities}) First, compute $S^{n+\myhalf}$ and $\beta_0^{n+\myhalf}$ using
\begin{equation}
S^{n+\myhalf} = \frac{S^n + S^{n+1,{\rm pred}}}{2}, \qquad \beta_0^{n+\myhalf} = \frac{\beta_0^n + \beta_0^{n+1,{\rm pred}}}{2}.
\end{equation}
Then, project $\uadvsdcstar$ to obtain $\uadvsdc$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^{n+\myhalf}\uadvsdc\right) = S^{n+\myhalf}.
\end{equation}

{\bf Step 2B:} ({\it Compute advective fluxes}) Use $\uadvsdc$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf}$, with iteratively-lagged reactions, explicit diffusion, and time-centered thermodynamic pressure as source terms.\\

{\bf Step 2C:} ({\it Compute diffusive fluxes}) Begin by computing the time-advanced density using
\begin{equation}
\frac{\rho^{n+1} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1}X_{k,{\rm AD}}^{n+1} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right] + I_{\rho X_k}^{\rm pred}.\label{eq:sdc species 3}
\end{equation}
Then, solve a backward-Euler-type correction equation for $h^{n+1}_{\rm AD}$,
\begin{eqnarray}
\frac{\rho^{n+1}h^{n+1}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf}\uadvsdc\right] + \uadvsdc\cdot\nabla p_0 + I_{\rho h}^{\rm pred}\nonumber\\
&& + \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1}_{\rm AD} + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n - \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^{n+1,{\rm pred}} k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla X_{k,{\rm AD}}^{n+1}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^{n+1,{\rm pred}}k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla p_0\right)\label{eq:sdc enthalpy 3}
\end{eqnarray}

{\bf Step 2D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}$ as the right hand side of (\ref{eq:sdc species 3}) without the $I_{\rho X_k}^{\rm pred}$ term, and define $Q_{\rho h}$ as the right hand side of (\ref{eq:sdc enthalpy 3}) without the $I_{\rho h}^{\rm pred}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{\rm lagged}$ and $I_{\rho h}^{\rm lagged}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the predictor in the next time step.\\

>>>>

{\bf Step 1B:} ({\it Compute advective fluxes}) Use $\uadvsdcpred$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf,{\rm pred}}$, with time-lagged reactions ($I^{n-1\rightarrow n}$), explicit diffusion, and time-centered thermodynamic pressure as source terms.  Define the advective flux divergences as
\begin{eqnarray}
A_{\rho X_k}^{\rm pred} &=& -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right],\\
A_{\rho h}^{\rm pred} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right].
\end{eqnarray}

{\bf Step 1C:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}} - \rho^n}{\Delta t} = \sum_mA_{\rho X_k}^{\rm pred}.
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}}X_{k,{\rm AD}}^{n+1,{\rm pred}} - (\rho X_k)^n}{\Delta t} = A_{\rho X_k}^{\rm pred} + I_{\rho X_k}^{n-1\rightarrow n}.\label{eq:sdc species 2}
\end{equation}
Then, solve a Crank-Nicolson-type diffusion equation for $h^{n+1,{\rm pred}}_{\rm AD}$, using transport coefficients evaluated at $t^n$ everywhere,
\begin{eqnarray}
\frac{\rho^{n+1,{\rm pred}}h^{n+1,{\rm pred}}_{\rm AD} - (\rho h)^n}{\Delta t} &=& A_{\rho h}^{\rm pred} + \uadvsdcpred\cdot\nabla p_0 + I_{\rho h}^{n-1\rightarrow n}\nonumber\\
&& + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n + \nabla\cdot\frac{\kth^n}{c_p^n}\nabla h_{\rm AD}^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_{k,{\rm AD}}^{n+1,{\rm pred}}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0\right).\label{eq:sdc enthalpy 2}
\end{eqnarray}

{\bf Step 1D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}^{\rm pred}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{\rho X_k}^{n-1\rightarrow n}$ term, and define $Q_{\rho h}^{\rm pred}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{\rho h}^{n-1\rightarrow n}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,{\rm pred}}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{\rm pred} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{\rm pred} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{n\rightarrow n+1,{\rm pred}}$ and $I_{\rho h}^{n\rightarrow n+1,{\rm pred}}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the corrector step.\\

{\bf Step 2:} ({\it Corrector}) In the corrector, we use the time-advanced state from the predictor to perform a more accurate integration of the thermodynamic variables.  The quantities $(S, \beta_0, k_{\rm th}, c_p, \xi_k, h_p)^{n+1,{n\rightarrow n+1,{\rm pred}}}$ are computed from $(\rho,\rho X_k,\rho h)^{n+1,{n\rightarrow n+1,{\rm pred}}}$.  This step is divided into several sub-steps:\\\\

{\bf Step 2A:} ({\it Compute advection velocities}) First, compute $S^{n+\myhalf}$ and $\beta_0^{n+\myhalf}$ using
\begin{equation}
S^{n+\myhalf} = \frac{S^n + S^{n+1,{n\rightarrow n+1,{\rm pred}}}}{2}, \qquad \beta_0^{n+\myhalf} = \frac{\beta_0^n + \beta_0^{n+1,{n\rightarrow n+1,{\rm pred}}}}{2}.
\end{equation}
Then, project $\uadvsdcstar$ to obtain $\uadvsdc$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^{n+\myhalf}\uadvsdc\right) = S^{n+\myhalf}.
\end{equation}

{\bf Step 2B:} ({\it Compute advective fluxes}) Use $\uadvsdc$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf}$, with iteratively-lagged reactions ($I^{n\rightarrow n+1,{\rm pred}}$), explicit diffusion, and time-centered thermodynamic pressure as source terms.  Define the advective flux divergences as
\begin{eqnarray}
A_{\rho X_k} &=& -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdcpred\right],\\
A_{\rho h} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf}\uadvsdcpred\right].
\end{eqnarray}

{\bf Step 2C:} ({\it Compute diffusive fluxes}) Begin by computing the time-advanced density using
\begin{equation}
\frac{\rho^{n+1} - \rho^n}{\Delta t} = -\sum_mA_{\rho X_k}.
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1}X_{k,{\rm AD}}^{n+1} - (\rho X_k)^n}{\Delta t} = A_{\rho X_k} + I_{\rho X_k}^{n\rightarrow n+1,{\rm pred}}.\label{eq:sdc species 3}
\end{equation}
Then, solve a backward-Euler-type correction equation for $h^{n+1}_{\rm AD}$,
\begin{eqnarray}
\frac{\rho^{n+1}h^{n+1}_{\rm AD} - (\rho h)^n}{\Delta t} &=& A_{\rho h} + \uadvsdc\cdot\nabla p_0 + I_{\rho h}^{n\rightarrow n+1,{\rm pred}}\nonumber\\
&& + \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1}_{\rm AD} + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n - \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^{n+1,{\rm pred}} k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla X_{k,{\rm AD}}^{n+1}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^{n+1,{\rm pred}}k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla p_0\right)\label{eq:sdc enthalpy 3}
\end{eqnarray}

{\bf Step 2D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}$ as the right hand side of (\ref{eq:sdc species 3}) without the $I_{\rho X_k}^{n\rightarrow n+1,{\rm pred}}$ term, and define $Q_{\rho h}$ as the right hand side of (\ref{eq:sdc enthalpy 3}) without the $I_{\rho h}^{n\rightarrow n+1,{\rm pred}}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{n\rightarrow n+1}$ and $I_{\rho h}^{n\rightarrow n+1}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the predictor in the next time step.\\
